---
title: "Author Compensation Monthly Performance Report"
author: "Brayden Ross, Senior Data Analyst"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    pdf_document: null
    theme: lumen
    toc: yes
    toc_float: yes
    code_folding: hide
  pdf_document:
    toc: yes
  html_notebook: 
    toc: yes
  
editor_options: 
  chunk_output_type: inline
---

<style>
.btn {
    padding: 6px 9px 4px;
    border-width: 1px 1px 1px 1px;
    background: linear-gradient(#EF4F34, #EB0586);
    font-size: 12px;
    font-weight: bold;
    text-transform: uppercase;
    color: #fff;
    border-radius: 4px;
}
btn-default {
    color: #fff;
    background-color: #fff;
    border-color: #fff;
    border-width: 1px 1px 1px 1px;
    border-radius: 4px;
}
.btn-default:hover, .btn-default:focus, .btn-group.open .dropdown-toggle.btn-default {
    background:linear-gradient(#EF4F34, #EB0586);
    border-color: #fff;
    border-width: 0 1px 1px 1px;
    color: #fff;
    border-radius: 4px;
}
.Main {
    padding-left: var(--sidebar-width);
    padding-top: calc(var(--header-height) + 40px);
    padding-bottom: 2rem;
    background: #fff;
}

.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
    z-index: 2;
    color: #ffffff;
    background: linear-gradient(#EF4F34, #EB0586);
    border-color: #EB0586;
    border-radius: 4px;
}
#toc > ul li a {
    display: block;
    color: #EF4F34;
    font-size: .9rem;
    padding-left: 0;
}
a:focus, a:hover {
    color: #EF4F34;
    text-decoration: underline;
}
.Sidebar {
    width: var(--sidebar-width);
    background: #fff;
    position: fixed;
    top: var(--header-height);
    bottom: 0;
    z-index: 9;
    overflow-y: auto;
    padding: 40px 0 30px;
    word-break: break-word;
}

.token.punctuation {
    color: #F57FA3;
}
.page-content h1, .page-content h2, .page-content h3, .page-content h4, .page-content h5, .page-content h6 {
    font-weight: 300;
    line-height: 1.2;
    color: #EF4F34;
}

.glyphicon {
    position: relative;
    top: 1px;
    display: inline-block;
    font-family: 'Glyphicons Halflings';
    font-style: normal;
    font-weight: 400;
    line-height: 1;
    color: #F57FA3;
    -webkit-font-smoothing: antialiased;
    -moz-osx-font-smoothing: grayscale;
}

p {
    font-size: 16px;
    line-height: 24px;
    margin: 0px 0px 12px 0px;
}

h1,h2{
    font-family: Arial, sans-serif;
    font-weight: 700;
    color: #000;
}

h3, h4, h5, h6, legend {
    font-family: Arial, sans-serif;
    font-weight: 700;
    color: #EF4F34;
}
.Content a, .page-content a, a {
    color: #EB0586;
    text-decoration: none;
}

element.style {
    font-weight: bold;
    color: #EF4F34 !important;
}

.tocify {
    width: 20%;
    max-height: 90%;
    overflow: auto;
    margin-left: 2%;
    position: fixed;
    border: 1px transparent;
    border-radius: 6px;
}
.tocify .tocify-item a, .tocify .list-group-item {
    padding: 5px 0;
    border-radius: 4px;
}
.dropdown-menu {
    position: absolute;
    top: 100%;
    left: 0;
    z-index: 1000;
    display: none;
    float: left;
    min-width: 160px;
    padding: 5px 0;
    margin: 2px 0 0;
    list-style: none;
    font-size: 14px;
    text-align: left;
    background:  linear-gradient(#fff, #fff) padding-box,
      linear-gradient(to right, #EF4F34, #EB0586) border-box;
    border: 1px solid transparent;
    border: 1px solid transparent;
    border-radius: 4px;
    box-shadow: 0 6px 12px rgba(0,0,0,0.175);
}
table {
    display: table;
    border-collapse: separate;
    border-spacing: 2px;
    border-color: grey;
    background:  linear-gradient(#fff, #fff) padding-box,
      linear-gradient(to right, #EF4F34, #EB0586) border-box;
    border: 2px solid transparent;
    border-radius: 4px;
}
pre {
    background:  linear-gradient(#fff, #fff) padding-box,
      linear-gradient(to right, #EF4F34, #EB0586) border-box;
    display: block;
    margin: 0 0 10px;
    font-size: 13px;
    line-height: 1.42857143;
    word-break: break-all;
    word-wrap: break-word;
    color: #333333;
    background-color: #f5f5f5;
    border-radius: 4px;
    border: 2px solid transparent;
}
b, strong {
    font-weight: bold;
    color: #EF4F34;
}
</style>

```{r,echo = FALSE, warning = FALSE, message = FALSE}
ps_orange <- "#EF4F34"
ps_pink <- "#F57FA3"
ps_purple  <- "#EB0586"
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.align = 'center')
library(kableExtra)
source('~/author_compensation/video/prod_framework/utilities.R')
prod_details <- snowflake_query("SELECT * FROM ANALYTICS.CERTIFIED.PX_CONTENT_COMPENSATION_DETAILS_WITH_FORECASTS_V2
                                WHERE USAGE_MONTH = DATEADD('MONTH',-2, DATE_TRUNC('MONTH',GETDATE())) AND FINAL_RATE > 0")
report_date <- unique(prod_details$usage_month)
prod_details$royalty_paid <- as.numeric(prod_details$royalty_paid)
```

# Report Introduction

This is a monthly summary report related to the previous months Author Compensation data and projections. The goal of this report is to identify the previous months performance in relation to both viewership projections as well as payment allocations to authors. In accompaniment to this report, additional resources are available pertaining to [historical payment/projection accuracy](https://pluralsight.atlassian.net/l/cp/vQcgfjwk) and [contextual understanding of Author Compensation's processes](https://pluralsight.atlassian.net/wiki/spaces/PE/pages/33155219493/Author+Compensation+Framework+and+Modeling). 

**Note that any courses with a 0% viewership rate assigned are not included in this analysis.**

**This report contains data for the month of **`r report_date`

## Report Contents

The report consists of the following topics, which are briefly explained:

* Viewership Statistics - Basic statistics and visualizations related to the previous months viewership are explored, both in relation to actual viewership recorded and viewership projected by the algorithm. Viewership error is also explored, relating to the proximity of the algorithms projections to what actually occurred in the given month.
* Payment Statistics - Basic statistics and visualizations related to the previous months viewership *payments* are explored, both in relation to actual payments to authors and projected payments generated by the Author Compensation framework. The error margin of these payments is also explored. 

# Viewership Statistics

In the last month:

* There were `r length(unique(prod_details$course_slug[prod_details$course_vt_perc != 0]))` course(s) with viewership recorded and `r length(unique(prod_details$course_slug[prod_details$course_vt_perc == 0]))` course(s) with no recorded viewership.
* The highest actual viewership % recorded was `r paste0(round(100 * max(prod_details$course_vt_perc), 2), '%')`, with the minimum actual recorded viewership % at `r paste0(100 * min(prod_details$course_vt_perc), '%')`.
  + The *expected* maximum viewership for the last month was `r paste0(round(100 * max(prod_details$predictions),2), '%')`, with the minimum *expected* viewership at `r paste0(round(100 * min(prod_details$predictions), 2), '%')`.
* The actual average viewership % for all `r length(unique(prod_details$course_slug))` courses was `r round(100 * mean(prod_details$course_vt_perc), 2)`%.

Below is the plotted distribution of actual viewership percentage opposed to the expected (projected) viewership % for the previous month:

```{r}
prod_details %>%
  ggplot() + geom_density(aes(x = predictions, color = 'Predictions'), size = 2) + 
  geom_density(aes(x = course_vt_perc, color = 'Actual Vt %'), size = 2) +
  theme_bw() + scale_color_manual(name = 'VT Type', values = c('Predictions' = ps_orange, 'Actual Vt %' = ps_purple)) + theme(text = element_text(size = 15))
```
## Viewership Error

In the last month:

* The Mean Absolute Error (MAE) for the predicted vs. actual viewership percentages was `r round(100 * caret::MAE(pred = prod_details$predictions, obs = prod_details$course_vt_perc), 2)`%
* The Root Mean Squared Error (RMSE) for the predicted vs. actual viewership percentages was `r round(caret::RMSE(pred = prod_details$predictions, obs = prod_details$course_vt_perc) * 100, 2)`%

The below plot visualizes the total viewership error for the respective course ages included in the previous months data. Reminder: the course age indicates the number of months between 1-24 that have passed since the course's publish date - patterns and model behaviors relating to specific course age spans are key to understanding the overall model performance:

```{r}
prod_details %>%
  group_by(course_age) %>%
  summarise(total_vt = sum(course_vt_perc),
            total_projections = sum(predictions)) %>%
  ggplot() + geom_line(aes(x = course_age, y = total_vt, color = 'Actual VT %'), size = 2) +
  geom_line(aes(x = course_age, y = total_projections, color = 'Predictions'), size = 2) +
  theme_bw() + xlim(1,24) + scale_color_manual(name = "VT Type", values = c('Predictions' = ps_orange, 'Actual VT %' = ps_purple)) + theme(text = element_text(size = 15))
```

The absolute percent error between the actual viewership recorded and the projected viewership totals for each course age present in the last month is shown below - note that any region in which the percent error exceeds a value of 1 indicates the model's over-projection for the total viewership in that course age category:

```{r}
prod_details %>%
  group_by(course_age) %>%
  summarise(total_vt = sum(course_vt_perc),
            total_projections = sum(predictions),
            perc_error = abs((total_projections - total_vt)/total_vt)) %>%
  ggplot() + geom_line(aes(x = course_age, y = perc_error), color = ps_orange, size = 2) +
  theme_bw() + xlim(1,24) + geom_hline(yintercept = 1, linetype = 'dashed', alpha = 0.8) + theme(text = element_text(size = 15))
```
```{r}
prod_details %>%
  group_by(course_age) %>%
  summarise(n_courses = n(),
            total_vt = sum(course_vt_perc),
            total_projections = sum(predictions),
            perc_error = abs((total_projections - total_vt)/total_vt)) %>%
  kbl(escape = F, caption = '<b>Payment Totals by Course Age with Percent Error<b>', label = c('Variable', NULL, 'Corr. Value')) %>%
  kable_styling(font_size = 15, full_width = F)
```



# Payment Statistics

In the last month: 

* The highest viewership payment was `r paste0('$', max(prod_details$royalty_paid))`, with a maximum *projected* payment of `r paste0('$', max(prod_details$course_exp_royalty))`. 
* The lowest viewership payment was `r paste0('$', min(prod_details$royalty_paid))`, with a minimum *projected* payment of `r paste0('$', min(prod_details$course_exp_royalty))`.
* The average payment amount was `r paste0('$', round(mean(prod_details$royalty_paid), 2))`, with a *projected* average payment of `r paste0('$', round(mean(prod_details$course_exp_royalty), 2))`.
* The total amount paid in royalties for the previous month was `r paste0('$',sum(prod_details$royalty_paid, na.rm = TRUE))`, with a *projected* total payment of `r paste0('$',sum(prod_details$course_exp_royalty, na.rm = TRUE))`.

## Payment Error

In the last month:

* The Mean Absolute Error (MAE) for the predicted vs. actual viewership percentages was `r paste0('$',round(caret::MAE(pred = prod_details$course_exp_royalty, obs = prod_details$royalty_paid), 2))`
* The Root Mean Squared Error (RMSE) for the predicted vs. actual viewership percentages was `r paste0('$',round(caret::RMSE(pred = prod_details$course_exp_royalty, obs = prod_details$royalty_paid), 2))`

The below plot visualizes the total payment error for the respective course ages included in the previous months data. Reminder: the course age indicates the number of months between 1-24 that have passed since the course's publish date - patterns and model behaviors relating to specific course age spans are key to understanding the overall model performance:

```{r}
prod_details %>%
  group_by(course_age) %>%
  summarise(total_paid = sum(royalty_paid),
            total_projections = sum(course_exp_royalty)) %>%
  ggplot() + geom_line(aes(x = course_age, y = total_paid, color = 'Actual Payment'), size = 2) +
  geom_line(aes(x = course_age, y = total_projections, color = 'Predictions'), size = 2) +
  theme_bw() + xlim(1,24) + scale_color_manual(name = "Payment Type", values = c('Predictions' = ps_orange, 'Actual Payment' = ps_purple)) + theme(text = element_text(size = 15))
```

```{r}
prod_details %>%
  group_by(course_age) %>%
  summarise(total_paid = sum(royalty_paid),
            total_projections = sum(course_exp_royalty),
            perc_error = abs((total_projections - total_paid)/total_paid)) %>%
  ggplot() + geom_line(aes(x = course_age, y = perc_error), color = ps_orange, size = 2) +
  theme_bw() + xlim(1,24) + geom_hline(yintercept = 1, linetype = 'dashed', alpha = 0.8) + theme(text = element_text(size = 15))
```
```{r}
prod_details %>%
  group_by(course_age) %>%
  summarise(n_courses = n(),
            total_paid = sum(royalty_paid),
            total_projections = sum(course_exp_royalty),
            perc_error = abs((total_projections - total_paid)/total_paid)) %>%
  kbl(escape = F, caption = '<b>Payment Totals by Course Age with Percent Error<b>', label = c('Variable', NULL, 'Corr. Value')) %>%
  kable_styling(font_size = 15, full_width = F)
```

## Payment Proximity to Target Levels

For each incoming content piece, internal targets are used to determine the optimal level of compensation Pluralsight hopes the Author to reach by the end of 36 months. A monthly target payment is assigned to each course based on its target, and statistics related to the proximity of the last months payments to their target amounts are explored below:

```{r, include = FALSE}
prod_details$payment_prox <- prod_details$royalty_paid - prod_details$course_avg_mnth_target
```


```{r}
prod_details %>%
  ggplot() + geom_density(aes(x = payment_prox), color = ps_orange, size = 2) + theme_bw() + theme(text = element_text(size = 15)) + ylab('Density') + xlab('Payment Proximity to Target') + labs(title = 'Payment Proximity Density')
```
The above figure shows the density of the proximity to the target payment for each course's recorded actual payment in the last month. The negative region depicts an *underpayment* below the desired level, while a positive value indicates the targeted amount was less than the actual amount earned.

```{r}
prod_details %>%
  summarise(`Total Overpaid` = sum(ifelse(payment_prox > 0, 1, 0)),
            `Total Underpaid` = n() - `Total Overpaid`) %>%
  kbl(escape = F, caption = '<b>Over/Underpaid Course Counts<b>', label = c('Variable', NULL, 'Corr. Value')) %>%
  kable_styling(font_size = 15, full_width = F)
```
